Paper_analyses

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
found an issue of missing heart rate data
almost all new neurotypicals 345-355 are misising practice heart rate data, and some clinical folks (606) are missing hr because their ecg was inverted wrongly

db_full4new_stim_screen_pupil_nopract_nt_304<- subset(db_full4new_stim_screen_pupil_nopract_nt, ssid_num>303)

@@

# alexithymia
table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_response))
pupil_arousal_findings$BIO_CDA.ISCR_TAS <- lmer(log(BIO_CDA.AmpSum +.1) ~ arousal_c+
                                             (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_basCor))
summary(pupil_arousal_findings$BIO_CDA.ISCR_TAS)
```

@@

nrow(db_full6new_hr_fix_stim_nt)+ nrow(db_HR_bio_final_346_355_withfix_stim)
# 6895
# nrow(bind_rows(db_full6new_hr_fix_stim_nt, db_HR_bio_final_346_355_withfix_stim))
db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix
db_full6new_hr_fix_stim_nt1<- bind_rows(db_full6new_hr_fix_stim_nt,
                                        db_HR_bio_final_346_355_withfix_stim)

@@

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
  group_by(ssid, tNo) %>%
  arrange(ssid, tNo,screencontent_no)%>%
  fill(Bio_Mean_HR_fix, .direction = "down")%>%
  subset(screencontent_no == 2)

@@

@@

>>>>

unique(db_full4new_stim_screen_pupil_nopract_nt$screencontent)
db_full4new_stim_screen_pupil_nopract_nt_304<- subset(db_full4new_stim_screen_pupil_nopract_nt, ssid_num>303)

@@

# phasic
unique(db_full4new_stim_screen_pupil_nopract_nt_304$ssid)

pupil_arousal_findings$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

summary(pupil_arousal_findings$BIO_CDA.PhasicMax)
anova(pupil_arousal_findings$arousal_phas_max)
interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)

interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred =valence_c , modx =  arousal_c)

# Global
unique(db_full4new_stim_screen_pupil_nopract_nt_304$ssid)

pupil_arousal_findings$BIO_Global.Mean <- lmer(log1p(BIO_Global.Mean+.1) ~ arousal_c * valence_c + (1|ssid)+ (1|stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

# TTP
table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_TTP.AmpSum))
pupil_arousal_findings$BIO_TTP.AmpSum <- lmer(log1p(BIO_TTP.AmpSum+.1) ~ arousal_c * valence_c + (1|ssid)+ (1|stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_304)

summary(pupil_arousal_findings$BIO_TTP.AmpSum)

anova(pupil_arousal_findings$arousal_phas_max)
interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)

interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred =valence_c , modx =  arousal_c)

# alexithymia
table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.PhasicMax))
interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)
pupil_arousal_findings$BIO_CDA.ISCR_TAS <- lmer(log(BIO_CDA.AmpSum +.1) ~ arousal_c+
                                             (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_basCor))
summary(pupil_arousal_findings$BIO_CDA.ISCR_TAS)

# table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304

# collapsed
```

@@

nrow(db_full6new_hr_fix_stim_nt)+ nrow(db_HR_bio_final_346_355_withfix_stim)
# 6895
# nrow(bind_rows(db_full6new_hr_fix_stim_nt, db_HR_bio_final_346_355_withfix_stim))
db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix

colnames(db_HR_bio_final_346_355_withfix_stim)
as.factor(db_HR_bio_final_346_355_withfix_stim$stimIAPS)
db_full6new_hr_fix_stim_nt$stimIAPS

db_HR_bio_final_346_355_withfix_stim

as.factor(db_HR_bio_final_346_355_withfix_stim$stim.x)
as.factor(db_HR_bio_final_346_355_withfix_stim$stim.y)
db_HR_bio_final_346_355_withfix_stim$stim.y<- NULL

unique(db_HR_bio_final_346_355_withfix_stim$screencontent)
unique(db_full6new_hr_fix_stim_nt$screencontent)
unique(db_full6new_hr_fix_stim_nt$screencontent.y)

db_full6new_hr_fix_stim_nt$screencontent.x<- NULL
db_full6new_hr_fix_stim_nt$screencontent.y<- NULL

unique(db_full6new_hr_fix_stim_nt$trialUnq.x)
unique(db_full6new_hr_fix_stim_nt$trialUnq.y)

db_full6new_hr_fix_stim_nt$trialUnq<- db_full6new_hr_fix_stim_nt$trialUnq.x
db_full6new_hr_fix_stim_nt$trialUnq.y<- NULL
db_full6new_hr_fix_stim_nt$trialUnq.x<- NULL

db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x

# bind heartrate old and new

db_full6new_hr_fix_stim_nt1<- bind_rows(db_full6new_hr_fix_stim_nt,
                                        db_HR_bio_final_346_355_withfix_stim)

table(is.na(db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR))
table(is.na(db_full6new_hr_fix_stim_nt$Bio_Mean_HR))

@@

table(is.na(db_full6new_hr_fix_stim_nt1$Bio_Mean_HR))

test<- subset(db_full6new_hr_fix_stim_nt1, is.na(Bio_Mean_HR))

unique(test$ssid)
# 606

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
  # mutate()
  group_by(as.numeric(ssid_num), as.numeric(tNo)) %>%
  arrange(ssid_num, as.numeric(tNo),as.numeric(screencontent_no))%>%
  # select(ssid, tNo,screencontent_no, Bio_Mean_HR,Bio_Mean_HR_fix)
  fill(Bio_Mean_HR_fix, .direction = "down")%>%
  subset(screencontent_no == 2)

@@

unique(db_full6new_hr_fix_stim_nt1.1$screencontent_no)

test<- subset(db_full6new_hr_fix_stim_nt1.1, is.na(Bio_Mean_HR_dif))

@@

# model

table(is.na(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif))
Bio_Mean_HR_dif_outl
